Life course and long-term perspectives of social inequality in mortality among

### 2017-09-22 article2.Rmd

---
title: Life course and long-term perspectives of social inequality in mortality among
  elderly and adults in Northern Sweden      1801–2013
author: "S&ouml;ren Edvinsson and G&ouml;ran Brostr&ouml;m"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---

>>>>

---
title: Life course and long-term perspectives of social inequality in mortality among
  elderly and adults in Northern Sweden      1801–2013
author: "S&ouml;ren Edvinsson and G&ouml;ran Brostr&ouml;m"
date: '`r Sys.Date()`'
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
fontsize: 12pt
citation_package: natbib
biblio-style: apalike
---
